USD Exchange Rate decreases during Election Anncouncement Period

### 2024-04-17 paper/paper.qmd
deleted an unused folder and update READMe and title of paper

---
title: "Effect of Election on Currency Fluctuation"
subtitle: "Analysis of USD Exchange Rate Fluctuation during Inaugurtion week"
author: 
  - Sandy Yu
thanks: "Code and data are available at: https://github.com/Jingying-yu/election-season-and-currency-fluctuation.git"
date: today
date-format: long
abstract: "This paper analyzes the effect of US Presidential Election Announcement and a change of political party on the USD exchange rate. Daily exchange rates gathered from FRED and past presidential inauguration dates from multiple government websites are used in a generalized linear regression model to estimate the effects. We find that election result announcement has an average negative effect on USD exchange rate whereas a change of political party contributes positively with a slightly larger magnitude. Our result suggests that exchange USD for another currency closly after a Presidential election with a change of political party could be profitable."
format: pdf
number-sections: true
toc: true
bibliography: references.bib
---

@@

Weaknesses and next steps should also be included.

>>>>

---
title: "USD Exchange Rate decreases during Election Anncouncement Period"
subtitle: "Analysis of USD Exchange Rate Fluctuation during Inaugurtion week"
author: 
  - Sandy Yu
thanks: "Code and data are available at: https://github.com/Jingying-yu/election-season-and-currency-fluctuation.git"
date: today
date-format: long
abstract: "This paper analyzes the effect of US Presidential Election Announcement and a change of political party on the USD exchange rate. Daily exchange rates gathered from FRED and past presidential inauguration dates from multiple government websites are used in a generalized linear regression model to estimate the effects. We find that election result announcement has an average negative effect on USD exchange rate whereas a change of political party contributes positively with a slightly larger magnitude. Our result suggests that exchange USD for another currency closly after a Presidential election with a change of political party could be profitable."
format: pdf
number-sections: true
toc: true
bibliography: references.bib
---

@@

- small effect size causing low explanitory power
- inauguration dates does NOT include presidential announcement results where the previous president gets re-elected for the next season, will cause bias in estimation.
